%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% A clean template for an academic CV. This is a short summary version.
%
% Uses tabularx to create two column entries (date and job/edu/citation).
% Defines commands to make adding entries simpler.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[9pt,a4paper]{article}

% Useful aliases
\newcommand{\TJU}{Tongji University}
\newcommand{\TP}{Télécom Paris}
\newcommand{\HDU}{Hangzhou Dianzi University}


% Identifying information
\newcommand{\Title}{Curriculum Vit\ae}
\newcommand{\FirstName}{Shuaifan}
\newcommand{\LastName}{Xia}
\newcommand{\Initials}{S}
\newcommand{\MyName}{\FirstName\ \LastName}
\newcommand{\Me}{\underline{\Initials. \LastName}}  % For citations
\newcommand{\Email}{shuaifan.xia@telecom-paris.fr}
\newcommand{\PersonalWebsite}{collin911.github.io/homepage}
\newcommand{\LabWebsite}{www.compgeolab.org}
\newcommand{\ORCID}{0000-0002-9769-4373}
\newcommand{\GitHubProfile}{collin911}

% Names for citing coauthors
\newcommand{\Lqw}{Q. Liu}
\newcommand{\Lmq}{M. Liu}
\newcommand{\Fw}{W. Fang}
\newcommand{\Jqw}{Q. Jiang}
\newcommand{\Lxz}{X. Li}
\newcommand{\Xml}{M. Xiong}
\newcommand{\Zsl}{S. Zhou}
\newcommand{\Xmy}{M. Xu}
\newcommand{\Dh}{H. Deng}



% Load packages
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Full Unicode support for non-ASCII characters
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[TU]{fontenc}

% Set main fonts
\usepackage[sfdefault]{atkinson}
\usepackage[ttdefault]{sourcecodepro}

% Icon fonts
\usepackage{fontawesome5}
\usepackage{academicons}

% Disable hyphenation
\usepackage[none]{hyphenat}

% Control the font size
\usepackage{anyfontsize}

% For fancy and multipage tables
\usepackage{tabularx}
\usepackage{ltablex}

% For new environments
\usepackage{environ}

% Manage dates and times
\usepackage{datetime}

% Set the page margins
\usepackage{geometry}

% To get the total page numbers (\pageref{LastPage})
\usepackage{lastpage}

% Control spacing in enumerates
\usepackage{enumitem}

% Use custom colors
\usepackage[usenames,dvipsnames]{xcolor}

% Configure section titles
\usepackage{titlesec}

% Fancy header configuration
\usepackage{fancyhdr}

% Control PDF metadata and links
\usepackage[colorlinks=true]{hyperref}


% Template configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\geometry{%
  margin=12.5mm,
  headsep=0mm,
  headheight=0mm,
  footskip=5mm,
  includehead=true,
  includefoot=true
}

% Custom colors
\definecolor{mediumgray}{gray}{0.5}
\definecolor{lightgray}{gray}{0.9}
\definecolor{mediumblue}{HTML}{2060c2}
\definecolor{lightblue}{HTML}{a0c3ff}

% No indentation
\setlength\parindent{0cm}

% Increase the line spacing
\renewcommand{\baselinestretch}{1.1}
% and the spacing between rows in tables
\renewcommand{\arraystretch}{1.25}

% Remove space between items in itemize and enumerate
\setlist{nosep}

% Set the spacing and format of sections
\titleformat{\section}
  {\normalfont\Large\mdseries} % format
  {} % label
  {0pt} % separation (left separation for hang)
  {} % text before title
  [\titlerule] % text after title
\titlespacing*{\section}
  {0pt} % left pad
  {0.1cm} % before
  {0cm} % after

% Disable number of sections. Use this instead of "section*" so that the sections still
% appear as PDF bookmarks. Otherwise, would have to add the table of contents entries
% manually.
\makeatletter
\renewcommand{\@seccntformat}[1]{}
\makeatother

% Define a new environment to place all CV entries in a 2-column table.
% Left column are the dates, right column the entries.
\newcommand{\TablePad}{\vspace{-0.2cm}}
\NewEnviron{EntriesTableDuration}{
\TablePad
\begin{tabularx}{\textwidth}{@{}p{0.10\textwidth}@{\hspace{0.02\textwidth}}p{0.88\textwidth}@{}}
  \BODY
\end{tabularx}
\TablePad
}
\NewEnviron{EntriesTableYear}{
\TablePad
\begin{tabularx}{\textwidth}{@{}p{0.05\textwidth}@{\hspace{0.01\textwidth}}p{0.94\textwidth}@{}}
  \BODY
\end{tabularx}
\TablePad
}

% Macros to set the year and duration on the left column
\newcommand{\Duration}[2]{\fontsize{10pt}{0}\selectfont \texttt{#1-#2}}
\newcommand{\Year}[1]{\fontsize{10pt}{0}\selectfont \texttt{#1}}
\newcommand{\Ongoing}{on}
\newcommand{\Future}{future}

% Macros to add links and mark publications
\newcommand{\DOI}[1]{doi:\href{https://doi.org/#1}{#1}}
\newcommand{\Website}[1]{\href{https://#1}{#1}}
\newcommand{\Preprint}[1]{Preprint: \href{https://doi.org/#1}{#1}}
\newcommand{\GitHub}[1]{\faGithub{} \href{https://github.com/#1}{#1}}
\newcommand{\Data}[1]{\faChartBar{} doi:\href{https://doi.org/#1}{#1}}

% Define command to insert month name and year as date
\newdateformat{monthyear}{\monthname[\THEMONTH], \THEYEAR}

% Configure a fancy footer
\newcommand{\Separator}{\hspace{3pt}|\hspace{3pt}}
\newcommand{\FooterFont}{\footnotesize\color{mediumgray}}
\pagestyle{fancy}
\fancyhf{}
\lfoot{%
  \FooterFont{}
  \MyName{}
  \Separator{}
  \Title{}
}
\rfoot{%
  \FooterFont{}
  Last updated: \monthyear\today{}
  \Separator{}
  \thepage\space of\space \pageref*{LastPage}
}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{1pt}
\preto{\footrule}{\color{lightgray}}

% Metadata for the PDF output and control of hyperlinks
\hypersetup{
  colorlinks,
  allcolors=mediumblue,
  breaklinks=true,
  pdftitle={\Title{} - \MyName},
  pdfauthor={\MyName},
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\begin{minipage}[t]{0.5\textwidth}
  {\fontsize{20pt}{0}\selectfont\MyName}
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
  \begin{flushright}
    \Title{}
  \end{flushright}
\end{minipage}
\\[-0.1cm]
\textcolor{lightgray}{\rule{\textwidth}{3pt}}
\begin{minipage}[t]{0.75\textwidth}
  Website: \Website{\PersonalWebsite}
  \\
  Email: \href{mailto:\Email}{\Email}
  \\
  ORCID: \href{https://orcid.org/\ORCID}{\ORCID}
  \\
  Google Scholar: \href{https://scholar.google.com/citations?user=x4Y8uCAAAAAJ}{\MyName}
\end{minipage}
\begin{minipage}[t]{0.07\textwidth}
  %\begin{flushright}
    \textbf{Chinese} 
    \\
    \textbf{English} 
    \\
    \textbf{French} 
    \\
    %\textbf{German}
  %\end{flushright}
\end{minipage}
\begin{minipage}[t]{0.18\textwidth}
  \begin{flushright}
    Native Speaker
    \\
    TOEFL 107
    \\
    A2
    \\
    %Basic
  \end{flushright}
\end{minipage}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}

\begin{EntriesTableDuration}
  \Duration{2024}{\Ongoing}  &
  \textbf{Ingénieur in Computer Science}, \TP, Île-de-France, France.
  \\ & GPA: 3.93/4.0
  \\ & Core Courses: Parallel and Distributed Computing, Concurrent Programming
  %\DOI{10.6084/m9.figshare.16883689}
  \\
  \Duration{2022}{2025}  &
  \textbf{M.Eng in Computer Science}, \TJU, Shanghai, China.
  \\ & GPA: 4.83/5.0 Ranking: 1/48 \emph{Summa Cum Laude}
  \\ & Research Area: Internet of Things, Wireless Communication
  %\DOI{10.6084/m9.figshare.16882300}
  \\
  \Duration{2018}{2022}  &
  \textbf{B.Eng in Information Security}, \HDU, Zhejiang, China.
  \\ & GPA: 4.72/5.0 Ranking: 1/116 \emph{Summa Cum Laude}
  \\ & Core Courses: Computer Networks, Principles of Communication, Signals and Systems 
  %\DOI{10.6084/m9.figshare.963547}
  \\
  \Duration{2015}{2018}  &
  Hangzhou Xuejun Highschool, Zhejiang, China.
  
\end{EntriesTableDuration}


\iffalse
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Community Service}

\begin{EntriesTableDuration}
  \Duration{2024}{\Ongoing} & \textbf{Embaixador}, Rede Brasileira de Reprodutibilidade, \Website{www.reprodutibilidade.org}
  \\
  \Duration{2024}{\Ongoing} & \textbf{Advisory Council Member}, EarthArXiv, \Website{eartharxiv.org}
  \\
  \Duration{2022}{\Ongoing} & \textbf{Board Member}, Software Underground, \Website{softwareunderground.org}
  \\
  \Duration{2022}{2023} & \textbf{Advisory Committee Member}, pyOpenSci, \Website{www.pyopensci.org}
  \\
  \Duration{2019}{2022} & \textbf{Topic Editor}, Journal of Open Source Software, \Website{joss.theoj.org}
\end{EntriesTableDuration}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Open Research Software}

\begin{EntriesTableDuration}
  \Duration{2010}{\Ongoing} &
  \textbf{Fatiando a Terra} | \Website{www.fatiando.org}
  \newline
  \textit{Python tools for geophysical data processing, forward modeling, and inversion}
  \newline
  Role: Project founder, core developer, Steering Council Member
  \\
  \Duration{2017}{\Ongoing} &
  \textbf{The Generic Mapping Tools (GMT)} | \Website{www.generic-mapping-tools.org}
  \newline
  \textit{A data processing and mapping toolbox for the Earth, Ocean, and Planetary Science}
  \newline
  Role: Community stewardship advisor, set up the website + forum + GitHub workflow
  \\
  \Duration{2022}{\Ongoing} &
  \textbf{xlandsat} | \Website{www.compgeolab.org/xlandsat}
  \newline
  \textit{Load Landsat remote sensing scenes in Python and xarray}
  \newline
  Role: Creator and sole developer
  \\
  \Duration{2017}{2021} &
  \textbf{PyGMT} | \Website{www.pygmt.org}
  \newline
  \textit{A Python interface for the Generic Mapping Tools}
  \newline
  Role: Project founder, developer, advisor
  \\
  \Duration{2009}{2016} &
  \textbf{Tesseroids} | \Website{tesseroids.leouieda.com}
  \newline
  \textit{Forward modeling of gravitational fields in spherical coordinates}
  \newline
  Role: Creator and sole developer
\end{EntriesTableDuration}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Open Educational Resources}

\begin{EntriesTableYear}
  \Year{2022} &
  \textbf{A Quick Introduction to Machine Learning}.
  \GitHub{leouieda/ml-intro}.
  \\
  \Year{2023} &
  \textbf{Remote Sensing with Python}.
  \GitHub{leouieda/remote-sensing}.
  \\
  \Year{2023} &
  \textbf{Lithosphere Dynamics with Python}.
  \GitHub{leouieda/lithosphere}.
  \\
  \Year{2022} &
  \textbf{Terrestrial Gravimetry with Python}.
  \GitHub{leouieda/gravity-processing}.
\end{EntriesTableYear}
\fi

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Research Experience}

\begin{EntriesTableDuration}
  \Duration{2022}{\Ongoing} &
  \textbf{Resonant Beam System} %| \Website{www.fatiando.org}
  \newline
  \textit{Employing intra-cavity laser beam resonance to achieve high-efficiency wireless power transfer and communication}
  \newline
  Role: Project member, researcher, and simulation program developer.
  \\
  \Duration{2019}{2022} &
  \textbf{Insight Security}
  \newline
  \textit{An integrated network security solution for industrial control system}
  \newline
  Role: Project leader, system architect, and developer.
  \\

  
\end{EntriesTableDuration}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Publication Highlights}

\begin{EntriesTableYear}
  \Year{2025}  &
    \textbf{Integrated Sensing and Communication System Based on Radio Frequency Resonance Beam}.
    \newline
    Y. Guo, \Me, \Xml, \Lqw, \Zsl, \Fw, \Jqw, G. Yan, J. Mu.
    \newline
    Under submission to IEEE Transactions on Signal Processing. 
    arXiv:\href{https://arxiv.org/pdf/2501.18878}{2501.18878}.
    \\
  \Year{2025}  &
    \textbf{Mobile Self-Protection Resonant Beam SWIPT with Adaptive Phase Control}.
    \newline
    X. Wang, \Me, \Fw, \Lmq, \Xml, \Lqw, Z. Pan.
    \newline
    Accepted for publication in IEEE Internet of Things Journal.
    \\
  \Year{2024}  &
    \textbf{Frequency Division Duplexing Resonant Beam Communication}.
    \newline
    \Me, \Lqw, \Jqw, \Fw, \Lmq.
    \newline
    Major revision submitted to IEEE Transactions on Wireless Communications.
    %|
    %\Data{10.6084/m9.figshare.22672978}
    \\
  \Year{2024}  &
    \textbf{Millimeter-wave Resonant Beam SWIPT}.
    \newline
    \Me, \Jqw, \Fw, \Lqw, \Zsl, \Lmq, \Xml.
    IEEE Internet of Things Journal.
    \DOI{10.1109/JIOT.2024.3452121}
    Open science:
    \GitHub{Collin911/RF-RBSWIPT}
    %|
    %\Data{10.6084/m9.figshare.22672978}
    \\
  \Year{2023}  &
    \textbf{Auto-Protection for Resonant Beam SWIPT in 
    Portable Applications}.
    \newline
    \Me, \Lqw, \Lmq, \Fw, \Xml, Y. Bai, \Lxz.
    IEEE Internet of Things Journal.
    \DOI{10.1109/JIOT.2023.3298521}
    Open science:
    \GitHub{Collin911/Resonant-Beam-AutoPro}
    %|
    %\Data{10.6084/m9.figshare.22672978}
    \\
  \Year{2023}  &
    \textbf{NLOS Transmission Analysis for Mobile SLIPT Using Resonant Beam}.
    \newline
    \Lmq, \Me, \Xml, \Xmy, \Lqw, \Dh.
    IEEE Transactions on Wireless Communications.
    \DOI{10.1109/TWC.2023.3277593}
    \\
  \Year{2022}  &
    \textbf{Integrated Communication and Positioning With Resonant Beam}.
    \newline
    \Lmq, \Me, \Xml, \Xmy, \Fw, \Lqw.
    IEEE Transactions on Wireless Communications.
    \DOI{10.1109/TWC.2022.3173929}
    \\
\end{EntriesTableYear}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Patents}

\begin{EntriesTableYear}
  \Year{2023}  &
    \textbf{A Portable Auto-Protected Simultaneous Wireless Information and Power Transfer System}.
    \newline
    \Lqw, \Me, \Lmq, Y. Bai, S. Han, \Xmy, \Lxz.
    \newline
    CN Patent No.: CN116707652A. Under examination as to substance.
    \\
  \Year{2023}  &
    \textbf{A Barcode Scanning System based on Resonant Beam System}.
    \newline
    \Lqw, \Lxz, \Me.
    \newline
    CN Patent No.: CN1172773030A. Under examination as to substance.
    \\
  \Year{2023}  &
    \textbf{A Priority-based Dynamic Communication Resource Allocation Method and Apparatus}.
    \newline
    \Lqw, Y. Zhu, \Me, \Jqw, S. Shen.
    \newline
    CN Patent No.: CN116347634A. Under examination as to substance.
    \\
  \Year{2021}  &
    \textbf{An Intrusion Detetion Method and Apparatus based on Modbus Packet Reassembly}.
    \newline
    W. Yin, Q. Zheng, H. Hu, \Me, K. Ye, X. Zhang, L. Zhai, T. Wu.
    \newline
    CN Patent No.: CN114124447A. Patent granted in 2024.
    \\
  \Year{2020}  &
    \textbf{A Lightweight Certificate-Free Industrial Internet of Things Access Control Method and System}.
    \newline
    Q. Chen, T. Wu, Q. Zheng, L. Dong, C. Hu, \Me, et., al.
    \newline
    CN Patent No.: CN111526130A. Patent granted in 2021.
\end{EntriesTableYear}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Work Experience}

\begin{EntriesTableDuration}
  \Duration{2023}{2024}  &
  \textbf{Research Mentor}, Chase Education Technology Co., Ltd., Hubei, China.
  \newline  Mentor undergraduate students in 
  conducting research projects related to computer science.
  \\
  \Duration{2019}{2022}  &
  \textbf{Teaching Assistant}, \HDU, China.
  \newline  
    \textit{Signals and Systems}, 
    \textit{Steganography and Digital Watermarking}.
  \\
    \Duration{2021}{2022}  &
    \textbf{President of Student Union}, \HDU, China.
    \newline  
      Responsible for internal and financial affairs, 
      and the Dept. Cultural \& Academic Activities.
\end{EntriesTableDuration}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Honors}

\begin{EntriesTableYear}
  \Year{2024} & 
    \textbf{France Excellence EIFFEL Scholarship}.
    Campus France, France.
  \\
  \Year{2024} & 
    \textbf{National Scholarship for Master Students}.
    Ministry of Education, China.
  \\
   \Year{2023} & 
    \textbf{Honorable Mention of Excellent Graduate Students}.
    Tongji University, Shanghai, China.
  \\
  \Year{2023} & 
    \textbf{National Scholarship for Master Students}.
    Ministry of Education, China.
  \\
  \Year{2022} & 
    \textbf{Valedictorian of the University Graduation Ceremony}.
    Hangzhou Dianzi University, Zhejiang, China.
  \\
  \Year{2022} & 
    \textbf{University Scholarship for Meritorious Graduates}.
    Hangzhou Dianzi University, Zhejiang, China.
  \\
  \Year{2021} & 
    \textbf{Zhejiang Provincial Scholarship}.
    Department of Education, Zhejiang, China.
  \\
  \Year{2021} & 
    \textbf{Top-10 Students of the Year}.
    Hangzhou Dianzi University, Zhejiang, China.
  \\
    \Year{2020} & 
      \textbf{National Scholarship for Undergraduate Students}.
      Ministry of Education, China.
  \\
    \Year{2019} & 
      \textbf{Zhejiang Provincial Scholarship}.
      Department of Education, Zhejiang, China.
\end{EntriesTableYear}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Awards \& Grants}

\begin{EntriesTableYear}
  \Year{2021} & 
    \textbf{\emph{FLTRP-ETIC Cup} English Reading Comprehension Contest}.
    \newline 
    First Prize in Zhejiang Province, China.
  \\
  \Year{2021} & 
    \textbf{Interdisciplinary Contest in Modeling (ICM)}.
    \newline
    Topic: Exploration of the Impact Factors for Music Trending - A Graph-based Approach.
    \newline
    Honorable Mention, USA.
  \\
  \Year{2021} & 
    \textbf{China College Computer Competition (C4)}.
    \newline
    Topic: Integrative Security Solution for Industrial Networks and the Internet of Things.
    \newline
    Second Prize in Easter China Division, China.
  \\
  \Year{2021} & 
    \textbf{\emph{Challenge Cup} College Scientific Innovation Contest}.
    \newline
    Topic: Cloud-Edge-Terminal Collaborative Security Protection for the Internet of Things.
    \newline
    Third Prize in Zhejiang Province, China.
  \\
  \Year{2020} & 
    \textbf{\emph{Challenge Cup} College Entreoreneurship Contest}.
    \newline
    Topic: Cloud-Edge-Terminal Collaborative Security Protection for the Internet of Things.
    \newline
    Third Prize in Zhejiang Province, China.
  \\
  \Year{2020} & 
    \textbf{National Innovation Project Grants for College Students}.
    \newline
    Topic: Integrated Network Security System for Industrial Control System.
    \newline
    Accomplished project. Served as the \emph{project leader}.
  \\
  \Year{2019} & 
    \textbf{National Innovation Project Grants for College Students}.
    \newline
    Topic: Autonomous Intrusion Detection System for Industrial Control System.
    \newline
    Accomplished project. Served as the \emph{project leader}.
  \\
  \Year{2019} & 
    \textbf{Zhejiang Provincial \emph{Xinmiao} Talent Project Grants}.
    \newline
    Topic: Autonomous Firewall System for Industrial Control System.
    \newline
    Accomplished project. Served as the \emph{project leader}.
\end{EntriesTableYear}

\end{document}
